---
title: "hw01_zy2392"
author: "Stephen Yuan"
date: "9/27/2021"
output: html_document
---

```{r}
library(tidyverse) # Call library
```

# Problem1: 

This problem is intended to emphasize variable types and introduce coercion.

## a) Create DataFrame
```{r}
prob1_df = tibble(
    rd_sample = rnorm(10, mean = 0, sd = 1),
    vec_logic = ifelse(rd_sample > 0, TRUE, FALSE),
    vec_char = c("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("small","medium","large","small","small","medium","large","small","medium","large"))
)
```

## b) Find mean of each variable

### mean of each variable
```{r}
sample_mean = mean(pull(prob1_df, rd_sample))
logic_mean = mean(pull(prob1_df, vec_logic))
char_mean = mean(pull(prob1_df, vec_char))
factor_mean = mean(pull(prob1_df, vec_factor))
sample_mean
logic_mean
```
mean function only works for numeric and logical variable type, and it does not work for charcter and factor variable type.

## c) Convert data type
```{r}
attach(prob1_df)
sample_num = as.numeric(rd_sample)
logic_num = as.numeric(vec_logic)
char_num = as.numeric(vec_char)
factor_num = as.numeric(vec_factor)
detach(prob1_df)
```
logic type can be transformed into 0 if it is false and 1 if it is True; factor can be transformed into levels then take means of levels instead; character type cannot be transformed into numeric type and NAs will be introduced so mean cannot be calculated.

# Problem 2: 

This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

## a) Dscription of dataset
```{r}
data("penguins", package = "palmerpenguins")
penguins # we can obtain a basic understanding of penguins dataset: there are 8 varibales and          # 344 penguins record (rows of data) in total.
```

So there are totally `r ncol(penguins)` columns and `r nrow(penguins)` rows.

Specifically, variables include `r names(penguins)`.
```{r}
factor_features = c('island', 'species', 'sex')
apply(penguins[,factor_features], 2, unique)
```
There are 3 factor variables, with 3 levels for each variable.

```{r}
numercal_features = c('bill_length_mm', 'bill_depth_mm', 'flipper_length_mm', 'body_mass_g', 'year')
apply(penguins[, numercal_features], 2, median, na.rm = TRUE)
```
There 5 numeric variables, and their medians are given as well.

Finally the mean of flipper length is `r round(mean(pull(penguins,flipper_length_mm), na.rm = TRUE),2)`.

## b) Scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, col = species)) + geom_point()
```

```{r}
ggsave('bill_vs_flipper.pdf', height=8, width=8)
```
