---
title: "tidy data"
output: github_document
---

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse) #tidyverse contains a variaty of packages including dplyr
library(readxl)
library(haven)
```

## `pivot_longer`:列变行

Load the PULSE data

```{r}
pulse_data = 
  haven::read_sas("./dimport_ex/public_pulse_data.sas7bdat") %>%
  janitor::clean_names()
```

Wide format to long format ... 

```{r}
pulse_data_tidy = 
  pulse_data %>%
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    names_prefix = "bdi_score_", #删掉了前缀bdi_score_
    values_to = "bdi"
  )
```

rewrite, combie, and extend (to add a mutate)

```{r}
pulse_data = 
  haven::read_sas("./dimport_ex/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
    pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    names_prefix = "bdi_score_",
    values_to = "bdi"
  ) %>%
  relocate(id, visit) %>%
  mutate(visit = recode(visit,"bl" = "00m")) #把visit列里面的bl的数值名换成00m
```

## `pivot_wider`:行变列

(never use `spread()`, always use `pivot_wider()`)

Make up some data!

```{r}
?pivot_wider
analysis_df = 
  tibble(
    group = c("treatment","treatment","placebo","placebo"),
    time = c("pre","post","pre","post"),
    mean = c(4, 8, 3.5, 4)
  )

analysis_df %>%
  pivot_wider(
    names_from = "time", 
    values_from = "mean"
  ) %>%
  knitr::kable() #让表格呈现的更可观
```

## Binding rows

Using the LotR data.

First step: import each table.

```{r}
fellowship_ring = 
  readxl::read_excel("./dimport_ex/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = 
  readxl::read_excel("./dimport_ex/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = 
  readxl::read_excel("./dimport_ex/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")
```

Bind all the rows together

(never use `rbind()`, always use `bind_rows()`)

```{r}
lotr_tidy = 
  bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  relocate(movie) %>%
  pivot_longer(
    female:male,
    names_to = "gender",
    values_to = "words"
  )
```

## Joing datasets

Import the FAS datasets.

```{r}
pups_df = 
  read_csv("./dimport_ex/FAS_pups.csv") %>%
  janitor::clean_names() %>% 
  mutate(sex = recode(sex, `1` = "male", `2` = "female")) 

litters_df = 
  read_csv("./dimport_ex/FAS_litters.csv") %>%
  janitor::clean_names() %>%
  relocate(litter_number) %>%
  separate(group, into = c("dose","day_of_tx"), sep = 3)

```

Next up, time to join them!

```{r}
fas_df = 
  left_join(pups_df, litters_df, by = "litter_number") %>%
  arrange(litter_number) %>%
  relocate(litter_number, sex, dose, day_of_tx)
```





