---
title: "Data Visualization 1"
author: "Stephen Yuan"
date: "10/4/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.height = "90%"
)
```

## Load the weather 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10, # 最低温
    tmax = tmax / 10) %>% # 最高温
  select(name, id, everything())
```

## Scatterplots!!

Create my first scatterplot ever.

```{r, warning = FALSE}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot ...

Start with the same ont and make it fancy!

```{r add color by city name}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(aes(color = NULL), se = FALSE)
```

What about the `aes` placement...

```{r only left the blue line}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) + 
  geom_smooth()
```

Lets facet some things!!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = .2) +
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(. ~ name) #按name分图
```

Lets combine some elements and try a new plot.

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

## Some small notes

How many geoms have to exist?

You can have whatever geoms you want.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

2D picture

```{r install package hexbin}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_bin_2d() # 2D图
```

You can use a neat geom!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .3)
```

## Use data manipulation

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(tmax = tmax*(9 / 5) + 32,
         tmin = tmin*(9 / 5) + 32)
```


## Univeriate plots

Histograms are really great.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color ...

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

Lets try a new geometry

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .1) # alpha = 颜色深度, 先配合分类
```

What about the plots ??

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_boxplot(alpah = .3)
```

Trendy plots .. violin box

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary()
```

Ridge plots -- the most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges(alpha = .8, scale = .8)
```


## Save and Embed

Lets save a scatterplot.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("./weather_plot.pdf", weather_plot, width = 8, height = 5)
```

What about embedding..

```{r, fig.width = 6, fig.height = 3}
weather_plot
```

```{r, fig.width = 12, fig.height = 6}
weather_plot
```

```{r, fig.width = 20, fig.height = 5}
weather_plot
# test
```















