---
title: "case study"
author: "Stephen Yuan"
date: "10/14/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)
```

## Load a dataset

```{r}
data("nyc_airbnb")
```

* Is price correlated with review score?
* which neighboorhod is most popular? Most expensive?
* Is availability related to proce?
* which neighborhood has the hightest view?
* Is room type related to neightborhood?
* Is length of stay related to neighborhood group?
* 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```

Lets try to count things:

```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

1. Is price correlated with review score?

```{r}
nyc_airbnb %>% 
  mutate(price = price / 1000) %>%
  mutate(price = as.integer(price)) %>% 
  mutate(stars = as.factor(stars)) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  cor(price, stars)
```

price and room type .. 

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + geom_point() + facet_grid(. ~ room_type)
```

price and neighborhood .. 

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarise(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighborhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + geom_boxplot() + coord_flip()
```

Price vs Location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) + geom_point(alpha = .5)
```


## retry leaflet for mapping

```{r, eval=FALSE}
pal = colorNameric("viridis",NULL)

nyc_airbnb %>% 
  filter(borough == "Manhattan", price < 500) %>% 
  sample_n(200) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
```




